\section{Let's Begin}
\subsection{Create a new Project}
Go to \url{https://scratch.mit.edu} and click "Create" in the top bar.
This will start a new project.

Next you need to rename your project from Unititled to something more relevant, like this:
\pic{0201-rename}

\subsection{Replace the Main Sprite}
I want a flappy bird, not a cat, so let's remove the default cat sprite:
\pic{0202-delete}
...and replace it with a different sprite.
\pic{0203-newsprite}
 I chose this parrot, feel free to choose another animal if you want. (or draw one if you're feeling adventurous!)
 \pic{0204-parrot}
 This is a bit big, so select shrink tool and click on the bird 15 times to shrink it to a better size.
 \pic{0205-shrink}
 
 \subsection{Replace the Background}
 Next up is to replace that boring background with something more fun. 
 \pic{0206-stage}
 I chose the Blue Sky background as I think it fits with my parrot, but again, feel free to customise and choose your own background.
 \pic{0207-bluesky}
 
 \subsection{Create the Obstacles}
 The last thing we need to do before we start scripting is create the sprite for our obstacles.
 \pic{0208-paintnew}
 We need a few different costumes for the obsacles pipe, so we can vary between them.

 \pic{0211-three}
  
Hint: if you want your obstacles to look the same, you can use the duplicate tool: \pic{0210-duplicate} before erasing a gap.

 
 \vfill
 
  It's your game, change the artwork to be whatever you want, from butterflies dodging flowers to spaceships avoiding planets.
 
 \vfill
 
 Be creative!
 

\vfill\vfill\vfill\vfill